*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-15 Code/Manuscript_O2.Rmd
working on captions

LabeledMC_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
                      "Spectral wavebands and light levels are individually controlled for each culture tube.",
                      "Real time Optical Density (OD) measurements eliminate intrusive subsampling of sterile cultures.",
                      "The temperature of culture tubes are controlled via heating or cooling of the aquarium water.",
                      "Gas with specific oxygen concentrations are bubbled through a humidifier and passed through a 0.2 um filter.",

>>>>

LabeledMC_cap <- glue("**PSI MCMIX-OD Multicultivator.**",
                      "Spectral wavebands and light levels are individually controlled for each culture tube.",
                      "Real time Optical Density (OD) measurements eliminate intrusive subsampling of sterile cultures.",
                      "The temperature of culture tubes are collectively controlled via heating or cooling of the aquarium water.",
                      "Gas with specific oxygen concentrations is bubbled through a humidifier and passed through a 0.2 um filter.",
